FourierTools.jl - Working with Fourier Space

### 2022-05-05 paper/paper.tex
Compiles again and changed to captionbox

\usepackage{hyperref}
%\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{graphicx}
%\usepackage[font=small,labelfont=bf]{caption}
\usepackage{subcaption}

@@

    \subsection{Shearing and Rotation}
        \autoref{fig:shearandrotation} shows the results of shearing and rotating an image.
        The image is provided by \verb|TestImages.jl|\footnote{\url{https://github.com/JuliaImages/TestImages.jl}}.
        Since we do not resize the image before, the shearing happens completely within the boundaries of the image.
        This circular property is induced by the circularity assumption of the DFT itself.
        The rotated image has even more complex patterns in the boundary regions.
        The reason is that the rotation is based on three shears and hence 
        each shear introduces circular artifacts which are shifted again by following shearing.
        \begin{figure}[h]
            \subcaptionbox{Sheared by \SI{150}{px}.\label{fig:sheared}}{\includegraphics[width=.23\textwidth]{figures/img_sheared.png}}
            \subcaptionbox{Rotated by \SI{50}{\degree}.\label{fig:rotated}}{\includegraphics[width=.23\textwidth]{figures/img_rotated.png}}
            \caption{Mandril testimage.}
            \label{fig:shearandrotation}
        \end{figure}
        Fortunately, those artifacts are completely revertible\footnote{in some case the shifting exponential multiplies with $0$ which cannot be recovered.}.
        To rotate without such boundary artifacts, one has to pre-allocate a suitable array beforehand.

>>>>

\usepackage{hyperref}
%\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{graphicx}
%\usepackage[font=small,labelfont=bf]{caption}
\usepackage{caption}

@@

    \subsection{Shearing and Rotation}
        \autoref{fig:shearandrotation} shows the results of shearing and rotating an image.
        The image is provided by \verb|TestImages.jl|\footnote{\url{https://github.com/JuliaImages/TestImages.jl}}.
        Since we do not resize the image before, the shearing happens completely within the boundaries of the image.
        This circular property is induced by the circularity assumption of the DFT itself.
        The rotated image has even more complex patterns in the boundary regions.
        The reason is that the rotation is based on three shears and hence 
        each shear introduces circular artifacts which are shifted again by following shearing.
        \begin{figure}[h]
            \captionbox{Sheared by \SI{150}{px}.\label{fig:sheared}}{\includegraphics[width=.23\textwidth]{figures/img_sheared.png}}
            \captionbox{Rotated by \SI{50}{\degree}.\label{fig:rotated}}{\includegraphics[width=.23\textwidth]{figures/img_rotated.png}}
            \caption{Mandril testimage.}
            \label{fig:shearandrotation}
        \end{figure}
        Fortunately, those artifacts are completely revertible\footnote{in some case the shifting exponential multiplies with $0$ which cannot be recovered.}.
        To rotate without such boundary artifacts, one has to pre-allocate a suitable array beforehand.
